Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-19 mu/article/article.tex
Changing working station

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
    range, and two local maxima from 1.90\,eV to 1.93\,eV and  1.96\,eV to
    2.0\,eV, in the visible, all for polarization angles between $25^{\circ}$
    and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$  for the
    \emph{alt} structure. A local maximum and the absolute maximum are located
    for the energy ranges from 0.67\,eV to 0.73\,eV and 0.90\,eV to 0.93\,eV and
    both for polarization angles between $120^{\circ}$ and $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

@@

    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
    photon energy and polarization angle $alpha$ for the \emph{up} structure.
    The absolute maxima of both are localized in the energy range from 0.08\,eV
    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}

@@

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The local maxima
    of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 1.95\,eV to 2.00\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
    \label{fig:up-vx-comp-rtp-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
    \label{fig:up-vy-comp-rtp-2}

@@

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{alt} structure. The absolute
    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 0.90\,eV to 0.93\,eV and for polarization angles from
    120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d-vva}
\end{figure}

>>>>

    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$ for the
    \emph{up} structure for two energy ranges. The absolute maxima is located
    for an energy range from 0.08\,eV to 0.10\,eV, in the Far Infrared radiation
    range, and two local maxima from 1.90\,eV to 1.93\,eV and from 1.96\,eV to
    2.0\,eV, in the visible radiation range, all for polarization angles between $25^{\circ}$
    and $50^{\circ}$.}
    \label{fig:up-3d-vsz}   
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response
    as a function of the photon energy and polarization angle $\alpha$  for the
    \emph{alt} structure. The local and the absolute maxima are located in the
    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
    respectively, and both in the Near Infrared and for polarization angles
    between $120^{\circ}$ and $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

@@

    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
    photon energy and polarization angle $\alpha$ for the \emph{up} structure.
    The absolute maxima of both are localized in the energy range from 0.08\,eV
    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}

@@

    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
    the photon energy and polarization angle $\alpha$ for the \emph{up}
    structure. Two local maxima of both responses are localized in the energy
    range from 1.90\,eV to 1.93\,eV and from 1.96\,eV to 2.0\,eV, in the visible
    radiation range, and for polarization angles between $25^{\circ}$ and
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}
    \label{fig:up-vx-comp-rtp-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}
    \label{fig:up-vy-comp-rtp-2}

@@

    \caption{$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ (top panel) and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (bottom panel)  as a function of
    the photon energy and polarization angle $\alpha$ for the \emph{alt}
    structure. The local and the absolute maxima are located in the
    energy ranges from 0.67\,eV to 0.73\,eV and from 0.90\,eV to 0.93\,eV,
    respectively, and both in the Near Infrared and for polarization angles
    between $120^{\circ}$ and $150^{\circ}$.}
    \label{fig:alt-3d-vva}
\end{figure}
